An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-26 poly-embed-journal/poly-embed-journal.tex
meeting notes

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^{|\Y| + 1}_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.

@@

\begin{claim}
  $\theta(v) = \pi(F_v) \cap \simplex$.
\end{claim}
\begin{proof}
  Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}

@@

\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
\end{claim}
\begin{proof}
\jessie{TODO}  
\end{proof}

@@

\begin{claim}
  \jessie{(6)}
  The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.
\end{claim}
\begin{proof}
  From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
  Each element of $\Lambda$ is $\pi(F_v)$ for some $v \in \V^*$.
  Take $r \in \R^*$ so that $v = L(r)$.
  By Claim~\ref{claim:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
  The result follows.
\end{proof}

>>>>

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.

@@

\begin{claim}
  \raf{Add quantifiers!} $\theta(v) = \pi(F_v) \cap \simplex$.
\end{claim}
\begin{proof}
  Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}

@@

\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
\end{claim}
\begin{proof}
  \jessie{TODO}
  \raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
\end{proof}

@@

\begin{claim}
  \jessie{(6)}
  $\Theta = \{\Gamma_r \mid r\in\R, \dim(\Gamma_r) = |\Y|-1\}$.
  \raft{The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.}
\end{claim}
\begin{proof}
  From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
  Each element of $\Lambda$ is $\pi(F_v)$ for some $v \in \V^*$.
  Take $r \in \R^*$ so that $v = L(r)$.
  By Claim~\ref{claim:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
  The result follows.
\end{proof}
